\thesistitle

### 2019-07-18 sections/background.tex
y u do dis :(
...
Playing with colors

\begin{figure}[H]
	\centering
	\includegraphics[width=1\textwidth]{img/clone-pair}
	\caption{Example of a clone pair, as found in the \href{https://github.com/Widen/valet}{Valet} project.}
	\label{fig:clonepair}
\end{figure}

Figure \ref{fig:cloneclass} displays a clone class with three clone instances.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\textwidth]{img/clone-class}
	\caption{Example of a clone class, as found in the \href{https://github.com/Widen/valet}{Valet} project.}
	\label{fig:cloneclass}
\end{figure}

>>>>

\newcommand{\highlightYellow}{\makebox[0pt][l]{\color{yellow}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightBlue}{\makebox[0pt][l]{\color{blue}\rule[-4pt]{1\linewidth}{14pt}}}
\newcommand{\highlightPurple}{\makebox[0pt][l]{\color{purple}\rule[-4pt]{1\linewidth}{14pt}}}
\begin{figure}
\begin{parcolumns}{3}
\colchunk[1]{
\begin{javacode}
// File1.java
|\highlightPurple|doA();
|\highlightPurple|doB();
|\highlightBlue|doC();
\end{javacode}}
\colchunk[2]{
\begin{javacode}
// File2.java
|\highlightPurple|doA();
|\highlightPurple|doB();
|\highlightBlue|doC();
\end{javacode}}
\colchunk[3]{
\begin{javacode}
// File3.java
|\highlightYellow|doA();
|\highlightYellow|doB();
doD();
\end{javacode}}
\end{parcolumns}
\caption{Two clone classes: One clone class with three clone instances and one with two clone instances.}
\end{figure}
